Jane, John … Leslie? A Historical Method for Algorithmic Gender Prediction

### 2015-12-02 article.Rmd
Fix incorrect example of editors

```{r, echo=FALSE}
editors <- data_frame(name = c("Madison", "Madison", "Morgan", "Morgan",
                               "Jan", "Jan"),
                      birth_year = c(1934, 1990, 1948, 1970, 1965, 1998))
```

```{r, echo=TRUE, results='markup'}
editors
```

>>>>

```{r, echo=FALSE}
editors <- data_frame(name = c("Madison", "Madison", "Morgan", "Morgan",
                               "Jan", "Jan"),
                      year = c(1934, 1990, 1948, 1970, 1965, 1998))
```

```{r, echo=TRUE, results='markup'}
gender_df(editors, method = "ssa")
```
